---
title: "Logistic Regression model for AHD"
author: "Huy N. Pham"
date: "4/11/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

The data table is the result from an cardiovascular (CV) study in Cleveland Clinic between May 1981 and September 1984. No patients had a history of CV disease. After providing the historical information, all patients performed a number of clinical tests. A part of features from these results was collected in the studying data table.

## Data loading

The data table was loaded and assigned to a variable call `data`.
```{r}
# Install the required library
list.of.packages <- c("dplyr", "qwraps2", "ggplot2", "gridExtra", "MASS")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)
library(qwraps2)
options(qwraps2_markup = "markdown")
library(dplyr)
library(ggplot2)
library(gridExtra)
library(MASS)

# Load the data table
data_link <- "https://github.com/pnhuy/datasets/raw/master/heart_uci/heart.csv"
heart <- read.csv(data_link)
```

## Exploratory Data analysis

The data have `r dim(heart)[1]` rows or patients, and `r dim(heart)[2]` fields: `r colnames(heart)`.

```{r}

# Remove the first column
data_col <- colnames(heart)
data_col <- data_col[data_col != "X"]
heart <- heart[data_col]

# Process the categorical variables
heart$Sex <- factor(heart$Sex, levels=c(0,1), labels=c('female', 'male'))
#heart$ChestPain <- factor(heart$ChestPain)
heart$Fbs <- factor(heart$Fbs)
heart$RestECG <- factor(heart$RestECG)
heart$ExAng <- factor(heart$ExAng)
heart$Slope <- factor(heart$Slope)
heart$Ca <- factor(heart$Ca)
heart$Thal <- factor(heart$Thal)
heart$AHD <- factor(heart$AHD)

factor_feature <- c("Sex", "Fbs", "RestECG", "ExAng", "Slope", "Ca", "Thal")
numberic_feature <- c("Age", "RestBP", "Chol", "MaxHR", "Oldpeak")
```

The basic statistics of data was below:
```{r results="asis"}
summary_table(heart)
```


The data might contain missing value and they would be removed before building the model.

```{r}
heart <- na.omit(heart)
```

After removing the NA, the table consisted of `r dim(heart)[1]` records.

The distibution of target (`AHD`) which was grouped by numerical variables was illustrated by using boxplot.
```{r}
p1 <- ggplot(heart, aes(x=AHD, y=Age, color=AHD)) + geom_boxplot() + theme(legend.position = "none") 
p2 <- ggplot(heart, aes(x=AHD, y=RestBP, color=AHD)) + geom_boxplot() + theme(legend.position = "none") 
p3 <- ggplot(heart, aes(x=AHD, y=Chol, color=AHD)) + geom_boxplot() + theme(legend.position = "none") 
p4 <- ggplot(heart, aes(x=AHD, y=MaxHR, color=AHD)) + geom_boxplot() + theme(legend.position = "none") 
p5 <- ggplot(heart, aes(x=AHD, y=Oldpeak, color=AHD)) + geom_boxplot() + theme(legend.position = "none") 
grid.arrange(p1, p2, p3, p4, p5)
```

The boxplot show the difference in distribution of `AHD` by `Age`, `MaxHR` and `Oldpeak`. These hypothesis would be tested by t-test. 

## Hypothesis testing

```{r}
t.test(Age ~ AHD, data=heart)
t.test(MaxHR ~ AHD, data=heart)
t.test(Oldpeak ~ AHD, data=heart)
```

The `t.test` show there was a significant difference in mean of `Age`, `MaxHR`, `Oldpeak` between group of patiend who had AHD or no AHD.

## Logistic regression model

A logistic model would be built to predict the probability of AHD by the remaining variables. Stepwise algorithm was used to select the best model.

```{r}
full.model <- glm(AHD ~ ., data=heart, family = "binomial")
step.model <- stepAIC(full.model, direction = "both", 
                      trace = FALSE)
summary(step.model)
```


## Interpret the Model


## Conclusion
