---
title: "R Notebook"
output:
  pdf_document: default
  html_notebook: default
  html_document:
    df_print: paged
---

Install and load helpful library for analysis.
```{r}
# Install required library, need not to re-install if you already have
# install.packages("dplyr")
# install.packages("Hmisc")
# install.packages("ggplot2")

# Load the require library
# library(dplyr)
# library(Hmisc)
# library(ggplot2)
```



# Data Loading & Exploratory data analysis

## Load the data in csv file and store to variable name `data`.
```{r Data_Loading}
path <- "https://raw.githubusercontent.com/pnhuy/datasets/master/heart_uci/heart.csv"
data <- read.csv(path)
```

## Show some rows of data to get some insight of data.
```{r}
head(data)
```

## Remove the first columns because it is not useful for analysis.
```{r}
data_col <- colnames(data)
data <- data[data_col[2:length(data_col)]]
head(data)
```

## What was the average age?
```{r}
mean(data$Age)
```

## From `sex` column, create new variable `gender` which only have 'male', 'female'?
```{r}
gender <- factor(data$Sex, levels=c(0,1), labels=c('female', 'male'))
```


## How many percent of patient who was male were there in the data?
```{r}
sum(data$Sex == 1)/length(data$Sex)*100
```

## How many percent of male patient who suffered heart disease were there in the data? What about female?
```{r}
print(sum(data[data$Sex == 1, 'AHD'] == 'Yes')/length(data[data$Sex == 1, 'AHD']))
print(sum(data[data$Sex == 0, 'AHD'] == 'Yes')/length(data[data$Sex == 0, 'AHD']))
```

## What was the range of RestBP?
```{r}
print(c(min(data$RestBP), max(data$RestBP)))
```

## What was the distribution of AHD?
```{r}
print(table(data$AHD))
```

## Calculate some basic desciptive statistics
```{r}
library(dplyr)
summary(data)
```

```{r}
library(Hmisc)
describe(data)
```

## Plot the distribution of AHD?
```{r}
barplot(table(data$AHD))
```

## Plot the distribution of RestBP per Sex?
```{r}
# In this plot, the distribution need a Factor variable to split, so we input the `gender`
# instead of `Sex`
ggplot(data, aes(x=RestBP)) + geom_histogram(aes(color=gender, fill=gender), alpha=0.2)
```


## Illustrate the relationship between sex and AHD?
```{r}
table(data$Sex, data$AHD)
```

## Illustrate the relationship between MaxHR and AHD?
```{r}
boxplot(data$MaxHR ~ data$AHD)
```

## Illustrate the relationship between Age and MaxHR?
```{r}
plot(data$Age, data$MaxHR)
```

## Illustrate the relationship between the continuous variables and the target?
```{r}
pairs(data[c('Age', 'RestBP', 'Chol', 'MaxHR', 'Oldpeak', 'AHD')])
```

# Hypothesis testing

## Compare the mean RestBP with normal BP (120)?
```{r}
t.test(data$RestBP, mu=120)
```

## Compare mean RestBP by AHD?
```{r}
RestBP_Yes = data[data$AHD == "Yes", "RestBP"]
RestBP_No = data[data$AHD == "No", "RestBP"]
t.test(RestBP_Yes, RestBP_No)
```

## Test the independence between AHD and Sex?
```{r}
chisq.test(data$Sex, data$AHD)
```


## Compare mean MaxHR by Thal
### ANOVA
```{r}
anova <- aov(MaxHR ~ Thal, data=data)
summary(anova)
```

### Pairwise T-Test
```{r}
pairwise.t.test(data$MaxHR, data$Thal)
```


### Tukey multiple pairwise-comparisons
```{r}
TukeyHSD(anova)
```

# Linear Regression

## Build a model to predict MaxHR by Age?
```{r}
model_1 <- lm(MaxHR ~ Age, data=data)
summary(model_1)
```

## Build a model to predict MaxHR by Age & RestBP & Thal?
```{r}
model_2 <- lm(MaxHR ~ Age + RestBP + Thal, data=data)
summary(model_2)
```

