---
title: "Review on R Programming"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

# Basic R
## Assignment and Evaluation

In `R`, we use `<-` symbol for assigning new variable.

```{r}
# Numerical variable
age <- 25

# String variable
name <- "John Doe"
```

R could be used as calculator:

### Arithmetic
```{r}
2 + 3
2 - 3
2 * 3
2 / 3
3 %% 2
2 ^ 3 
```

Exercise: calculate the expression and assign it to variable `result`: 
$$\sqrt[3]{\frac{435.4 \times 3.56}{(34 + 3)^2}}$$

### Advanced mathematical operators
```{r}
log(10) # natural logarit
log10(10) # logarit base ten
abs(-4) # absolute
sqrt(25) # square root
sum( 2 + 5) # summation
sin(pi)
cos(pi)
tan(pi)
```

### Comparison and logical operators
Comparative operators:
```{r}
a = 1
b = 2
a > b # greater than
a <= b # greater than or equal
a == b # equal
a != b  # not equal
```

Logical operators:
```{r}
a = TRUE
b = FALSE
class(a)
class(b)
a & b # a AND b
a | b # a OR b
!a # NOT a
```

## R Objects

R has 5 basic classes of objects:

* character (similar to string in other language)
* numeric (real numbers)
* integer
* complex (number)
* logical (or boolean)

```{r}
character_var <- "John"
numeric_var <- 3.14
integer_var <- 100L
complex_var <- 1 + 2i
logical_var <- TRUE
```

Vector is another popular type of R object. A vector can only contain objects of the same class.

```{r}
# Empty vector
a <- vector()
numeric_vector <- c(1, 2, 3)
character_vector <- c("Alice", "Betty", "Catheryn")
```

## Numbers in R
### Real number
```{r}
# Number
a <- 1
print(a)
print(class(a))
```

### Integer number
```{r}
i <- 100L
print(i)
print(class(i))
```

### Infinity
```{r}
q <- 1/0
print(q)
print(class(q))
```

### NaN - Not a number
```{r}
n <- 0 / 0
print(n)
print(class(n))
```

Also:
```{r}
m <- NaN
print(m)
print(class(m))
```

## Vectors
The `c()` function can be used to create a vectors.
```{r}
x <- c(0.5, 0.6) ## numeric
x <- c(TRUE, FALSE) ## logical
x <- c(T, F) ## logical
x <- c("a", "b", "c") ## character
x <- 9:29 ## integer
x <- c(1+0i, 2+4i) ## complex
```

You can also use the vector() function to initialize vectors.
```{r}
x <- vector("numeric", length = 10)
print(x)
```

### Mixing objects in R

Because the vector in R only accept one class for every members, the vectors with different data types will be implicitly coerced.
```{r}
a <- c(1.7, "a") ## character
print(a)
b <- c(TRUE, 2) ## numeric
print(b)
c <- c("a", TRUE) ## character
print(c)
```

### Explicit Coercion

We can do coercion by ourself.

```{r}
x <- 0:6
class(x)
as.numeric(x)
as.logical(x)
as.character(x)
```

However, the vectors sometimes can't do coercion. In this case, the NAs will be return.

```{r}
x <- c("a", "b", "c")
as.numeric(x)
as.logical(x)
as.complex(x)
```

## Matrices

### Create a new matrix

The matrix can be defined in R with `matrix` keyword.

```{r}
# Define an empty matrix
n <- matrix(nrow = 2, ncol = 3)
n

# Define a matrix from a range
m <- matrix(1:6, nrow = 2, ncol = 3)
m
# Display the dimension of m
dim(m)

# Display the attributes of m
attributes(m)
```


### Create matrix from vector

```{r}
m <- 1:10
m
dim(m) <- c(2, 5)
m
```

### Create matrix by binding

```{r}
x <- 1:3
y <- 10:12
```

#### Row binding

```{r}
rbind(x, y)
```

#### Column binding

```{r}
cbind(x, y)
```

## Reading & Writing Data in R

There are some principal function reading data in R:

* `read.table` and `read.csv` for reading tabular data (file `csv`, `txt`)
* `readLines` for reading lines of a text file

For writing:

* `write.table` for writing tabular data to text file (`csv`)
* `writeLines` for writing character data line-by-line to a file



